\Large\textbf{Advection versus diffusion in brain ventricular transport}

### 2025-04-07 paper/main.tex
Updates in Discussion preface.

\section{Discussion}
In this study, we have presented a computational model of CSF flow and
solute transport within brain ventricles.
We used the larval zebrafish brain ventricles since its geometry and
flow mechanisms are well described, thereby allowing us to validate
our simulations experimentally. Our computational framework can be adapted to
and implemented in other ventricular systems in the future,
once the flow parameters of such systems
are adequately resolved.
We assumed that intraventricular CSF flow was governed
by the Stokes equations.
By imposing tangential traction and normal pressure
on the CSF flow, we were able to reproduce flow fields with similar features
as observed experimentally. The prominent flow features were vortex-structured flow
mediated by cilia, and pulsatile flow mediated by the cardiac cycle.

Using the simulated CSF flow, we modeled solute transport by an advection-diffusion equation.
The transport results compared well with data from in vivo experiments in zebrafish.
Then, by using a computational model as well as zebrafish mutants with paralyzed cilia,
we identified that even though advection by cilia is dominant,
diffusion plays a significant role in protein transport.
Finally, we investigated how local cilia paralysis and ventricular geometries
affect solute distribution. Altogether, we present not only new findings on the roles of
advection and diffusion in brain ventricular transport, but also provide a
computational framework to study CSF flow and transport in ventricular geometries.

>>>>

\section{Discussion}
In this study, we have presented a computational model of CSF flow and
solute transport within brain ventricles.  We used the larval
zebrafish brain ventricles since their geometry and flow mechanisms are
well described, thereby allowing for validation of the simulation
results against experimental measurements. Our computational framework
can be adapted to other ventricular systems, once the flow parameters
of such are adequately resolved. Here, we assumed that
intraventricular CSF flow was governed by the Stokes equations. By
imposing tangential traction and normal pressure acting on the CSF, we
were able to reproduce flow features observed experimentally. In
particular, vortex-structured flow mediated by the cilia and pulsatile
flow mediated by the cardiac cycle emerged as key flow characteristics.

Using the simulated CSF flow, we modeled solute transport via an
advection-diffusion equation. The resulting evolution and distribution
of solutes compared well with data from in vivo experiments in
zebrafish and is advection-dominated on the global scale for a
physiologically-relevant range of solutes. By studying the
distribution patterns in the absence of cilia motion, both via
zebrafish mutants and computationally, we find that diffusion more
strongly affects solute spread to distant parts of the ventricular
system (upstream). Regional loss of cilia delayed solute transport
with the most pronounced effect stemming from dorsal cilia
paralysis. Moreover, the ventricular morphology also affects solute
distribution, with the duct between the anterior and middle ventricles
as a key passage. Altogether, we present not only new findings on the
roles of advection and diffusion in brain ventricular transport, but
also provide a computational framework to study CSF flow and transport
in ventricular geometries.
